---
title: Geochemical Modelling of Ig. Processes - Chapter 3
author: Nguyen Cong Nghia
date: '2020-06-16'
slug: geochemical-modelling-of-ig-processes-chapter-3
categories:
  - R
tags:
  - geochemical modeling
  - geochemistry
  - Igneous processes
description: ''
featured: ''
featuredalt: ''
featuredpath: ''
linktitle: ''
output:
  blogdown::html_page:
    toc: true
---
This post is a compilation of the exercises from Chapter 3: Classical Plots from the book Geochemical Modelling of Igneous Processes - Principles and Recipes in R language by Vojtěch Janoušek, Jean Hervé Martin, Vojtěch Erban and Colin Farrow.
```{r}
sink("/dev/null"); suppressPackageStartupMessages(library(GCDkit)); sink();
```

### Binary Plots
#### Plotting Simple Binary Plots
In this exercise we focus on graphical analysis of the Sázava dataset.
a) Build a binary plot SiO2–CaO. Choose suitable ranges for the axes,label them and annotate data points by sample names. Assign the plotting symbols according to individual rock types (utilizing the pre-defined column “Symbol”).

b) Plot a line SiO2/CaO = 10 passing through origin [0,0].

c) Plot a diagram logZr – logBa and fit the data points,using the least-square linear regression, by a straight line.
```{r fig, fig.width = 10, fig.height = 5}
sazava <- read.table("data/sazava.data",sep="\t")
par(mfrow=c(1,2))
par(mar=c(4,4,1,1))
plot(sazava[,"SiO2"],sazava[,"CaO"], cex=1.2,
     xlab=expression(SiO[2]),ylab="CaO",
     pch=sazava[,"Symbol"],xlim=c(49,75),ylim=c(0,15))
text(sazava[,"SiO2"],sazava[,"CaO"],rownames(sazava),
     pos=4,cex=0.7)
abline(0,0.1)
plot(sazava[,"Zr"],sazava[,"Ba"],xlab="Zr",ylab="Ba",
     pch=15,cex=1.5,log="xy")
lq <- lm(log10(sazava[,"Ba"]) ~ log10(sazava[,"Zr"]))
lq
abline(lq,lty=2,lwd=2,col="darkgreen")
```


