---
title: R Syntax in a Nutshell III
author: Nguyen Cong Nghia
date: '2020-06-15'
slug: r-syntax-in-a-nutshell-iii
categories:
  - R
tags:
  - R basics
description: ''
featured: ''
featuredalt: ''
featuredpath: ''
linktitle: ''
output:
  blogdown::html_page:
    toc: true
---
### Programming in R
#### Input and Output
Typical print message:
```{r}
x <- 5.8
cat("The result is",x,"N/m.\n")
```
```{r}
x <- readline("Enter x: \n")
x
```
```{r}
x <- as.numeric(x)
x
```

### Conditional Execution
The traditional if... else... syntax in R
```{r}
x <- 6
y <- 0.5
if (x>2 & y<1){
  print(x)
  print(y)
}else{
  cat("Warning, x<=2 or y>-1\n")
}
```

### Loops
R has powerful indexing power, therefore loops are needed considerably less ofen than in any conventional programming language.
```{r}
for (f in seq(1,10,by=2)){
  cat("Square root of",f,"is",sqrt(f),"\n")
}
```
Try to avoid loops if possible. Here is an alternative of the above codes:
```{r}
x <- seq(1,10,by=2)
ee <- paste("Square root of",x,"is",sqrt(x),"\n")
cat(ee)
```
Commands *apply, tapply, sapply* are commonly a better approach.
#### User-defined Functions
**function.name** <- **function**(*argument1,argument2,...*)expression

For example: calculating a geometric mean, which defined as $n^{th}$ root of the product of n numbers:

$$S = \sqrt{\prod_{i = 1}^{n} f(x_i)}$$
```{r}
geo.mean <- function(x){
  z <- prod(x)^(1/length(x))
  return(z)
}
x = seq(1,100)
geo.mean(x)
```
Arguments to Functions

* Pass them in the order matching the function's definition 

* Supply the arguments in the form *argument.name = value* in an arbitrary sequence

```{r}
my.plot <- function(x,y,symb="+",color="red"){
  plot(x,y,pch=symb,col=color)
}
x = seq(1,20,1)
y = seq(5,24,1)
my.plot(x,y)
my.plot(x,y,"o")
my.plot(x,y,color="blue")
args("my.plot")
```
Assigments in Functions


