---
title: R Syntax in a Nutshell
author: Nguyen Cong Nghia
date: '2020-06-10'
slug: r-basics
categories:
  - R
tags:
  - R basics
output:
  blogdown::html_page:
    toc: true

---

### Seeking help
Here demonstrate how to seek help in R programing. These keywords include: help(), ?, apropos and example.
```{r}
help(plot)
?plot
apropos("plot") #Commands related to "plot"
example(plot)
```
### Numeric Vectors
#### Assignment
Assignment of several items to a vector is done using the combine function c:
```{r}
x <- c(10.4, 5.6, 3.1, 6.4, 21.7)
y <- c(x,0,x)
y
```
#### Vector Arithmetic
For vectors, calculations are made using basic arithmetic operators: + - * / ^. The use of these operators for two vectors of the same length is intuitive. In other cases, the elements of the shorter vector are recycled.
```{r}
print("Intuitive operators of same length vectors")
x*2
print("Multiply is recycled, i.e. *1 *2 *1 *2 *1")
x*c(1,2) 
```

#### Names
Each vector may have an attribute *names* (the length of the vector and names must be matching)
```{r}
x <- c(3,15,27)
names(x) <- c("Opx","Cpx","Pl")
x
```

